### 2019-07-09 README.Rmd
Update README.Rmd

[![badge](https://img.shields.io/badge/Launch-Analysis-lightblue.svg)](https://mybinder.org/v2/gh/seabbs/ExploreBCGOnOutcomes/master?urlpath=rstudio)
[![Paper](https://img.shields.io/badge/Paper-10.1101/366476-lightgrey.svg)](https://doi.org/10.1101/366476)
[![DOI](https://zenodo.org/badge/127124135.svg)](https://zenodo.org/badge/latestdoi/127124135)

>>>>

[![badge](https://img.shields.io/badge/Launch-Analysis-lightblue.svg)](https://mybinder.org/v2/gh/seabbs/ExploreBCGOnOutcomes/master?urlpath=rstudio)
[![Paper](https://img.shields.io/badge/Paper-10.1016/j.vaccine.2019.06.056-lightgreen.svg)](https://doi.org/10.1016/j.vaccine.2019.06.056)
[![Preprint](https://img.shields.io/badge/Preprint-10.1101/366476-lightgrey.svg)](https://doi.org/10.1101/366476)
[![DOI](https://zenodo.org/badge/127124135.svg)](https://zenodo.org/badge/latestdoi/127124135)
